Covariate analysis of ROSMAP reprocessed counts (with TMM and SVA normalisation)

### 2017-01-23 code/Rmd/MSSM_RNASeq_Reprocessed_TMM.Rmd
Minor bug fix
Added folder annotations to the markdown code

thisFileName <- 'MSBB_RNASeq_Reprocessed_TMM.Rmd'

# Github link
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='AMPAD')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```
### Data download
Data were obtained from AMP-AD portal of MSSM, and following brain regions were analysed for differential expression between case and control:
  | Region | Name                      | 
  | :----- | ------------------------- | 
  | BM_10  | Frontal Pole (FP)         |
  | BM_22  | Superior Temporal Gyrus   |
  | BM_36  | Parahipocampal Gyrus (PHG)|
  | BM_44  | inferior frontal Gyrus (IFG)|

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = 'MSBB Reprocessed RNASeq TMM', parentId = parentId)
CODE <- synStore(CODE)

>>>>

thisFileName <- 'MSSM_RNASeq_Reprocessed_TMM.Rmd'

# Github link
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='AMPAD')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```
### Data download
Data were obtained from AMP-AD portal of MSSM, and following brain regions were analysed for differential expression between case and control:
  | Region | Name                           | 
  | :----- | ------------------------------ | 
  | BM_10  | Frontal Pole (FP)              |
  | BM_22  | Superior Temporal Gyrus (STG)  |
  | BM_36  | Parahipocampal Gyrus (PHG)     |
  | BM_44  | inferior frontal Gyrus (IFG)   |

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = 'MSBB Reprocessed RNASeq TMM', parentId = parentId)
annotations(CODE) = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'Reprocessed RNAseq',

  tissueTypeAbrv	= 'FP, STG, PHG, IFG', 
  study = 'MSSM', 
  center = 'MSBB',

  organism = 'HomoSapiens',
  consortium	= 'AMP-AD',

  normalizationStatus	= TRUE,
  modelSystem	= FALSE,

  normalizationType	= 'TMM'
)
CODE <- synStore(CODE)

### 2017-01-23 code/Rmd/MSSM_RNASeq_Reprocessed_TMM_SVA.Rmd
Minor bug fix
Added folder annotations to the markdown code

library(parallel)
library(foreach)

@@

# Github link
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='AMPAD')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```
### Data download
Data were obtained from AMP-AD portal of MSSM, and following brain regions were analysed for differential expression between case and control:
  | Region | Name                      | 
  | :----- | ------------------------- | 
  | BM_10  | Frontal Pole (FP)         |
  | BM_22  | Superior Temporal Gyrus   |
  | BM_36  | Parahipocampal Gyrus (PHG)|
  | BM_44  | inferior frontal Gyrus (IFG)|

@@

# Residuals after normalisation
RESIDUAL.GENE_EXPRESSION = residuals.MArrayLM(FIT,VOOM.ADJUSTED.GENE_EXPRESSION$E)
```
`r tmp`
### SVA 
Estimate surrogate variables using SVA package
```{r sva}
MODEL0 = DM1$design[,-grep('BrodmannArea.CDR',colnames(DM1$design))] # Get null model by removing variable of interest
MODEL0 = MODEL0[,linColumnFinder(MODEL0)$indepCols]
MODEL1 = DM1$design
MODEL1 = MODEL1[,linColumnFinder(MODEL1)$indepCols]

@@

# Calculate correlation values of random effects
correlation = parallelDuplicateCorrelation(VOOM.ADJUSTED.GENE_EXPRESSION, block = COVARIATES$Donor_ID)

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = 'MSBB Reprocessed RNASeq TMM SVA', parentId = parentId)
CODE <- synStore(CODE)

>>>>

library(parallel)
library(foreach)
library(doMC)
library(doParallel)

@@

# Github link
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='AMPAD')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```
### Data download
Data were obtained from AMP-AD portal of MSSM, and following brain regions were analysed for differential expression between case and control:
  | Region | Name                           | 
  | :----- | ------------------------------ | 
  | BM_10  | Frontal Pole (FP)              |
  | BM_22  | Superior Temporal Gyrus (STG)  |
  | BM_36  | Parahipocampal Gyrus (PHG)     |
  | BM_44  | inferior frontal Gyrus (IFG)   |

@@

# Residuals after normalisation
RESIDUAL.GENE_EXPRESSION = residuals.MArrayLM(FIT,VOOM.ADJUSTED.GENE_EXPRESSION$E)
```
### SVA 
Estimate surrogate variables using SVA package
```{r sva}
MODEL0 = DM1$design[,-grep('BrodmannArea.CDR',colnames(DM1$design))] # Get null model by removing variable of interest
MODEL0 = MODEL0[,linColumnFinder(MODEL0)$indepCols]
MODEL1 = DM1$design
MODEL1 = MODEL1[,linColumnFinder(MODEL1)$indepCols]

@@

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = 'MSBB Reprocessed RNASeq TMM SVA', parentId = parentId)
annotations(CODE) = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'Reprocessed RNAseq',

  tissueTypeAbrv	= 'FP, STG, PHG, IFG', 
  study = 'MSSM', 
  center = 'MSBB',

  organism = 'HomoSapiens',
  consortium	= 'AMP-AD',

  normalizationStatus	= TRUE,
  modelSystem	= FALSE,

  normalizationType	= 'TMM and SVA'
)
CODE <- synStore(CODE)

### 2017-01-23 code/Rmd/Mayo_RNASeq_Reprocessed_TMM.Rmd
Added folder annotations to the markdown code

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = 'UFL_Mayo_ISB Reprocessed RNASeq TMM', parentId = parentId)
CODE <- synStore(CODE)

>>>>

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = 'UFL_Mayo_ISB Reprocessed RNASeq TMM', parentId = parentId)
annotations(CODE) = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'Reprocessed RNAseq',

  tissueTypeAbrv	= 'CBE, TCX', 
  study = 'MayoRNASeq', 
  center = 'UFL-MAYO-ISB',

  organism = 'HomoSapiens',
  consortium	= 'AMP-AD',

  normalizationStatus	= TRUE,
  modelSystem	= FALSE,

  normalizationType	= 'TMM'
)
CODE <- synStore(CODE)

### 2017-01-23 code/Rmd/Mayo_RNASeq_Reprocessed_TMM_SVA.Rmd
Added folder annotations to the markdown code

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = 'UFL_Mayo_ISB Reprocessed RNASeq TMM SVA', parentId = parentId)
CODE <- synStore(CODE)

>>>>

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = 'UFL_Mayo_ISB Reprocessed RNASeq TMM SVA', parentId = parentId)
annotations(CODE) = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'Reprocessed RNAseq',

  tissueTypeAbrv	= 'CBE, TCX', 
  study = 'MayoRNASeq', 
  center = 'UFL-MAYO-ISB',

  organism = 'HomoSapiens',
  consortium	= 'AMP-AD',

  normalizationStatus	= TRUE,
  modelSystem	= FALSE,

  normalizationType	= 'TMM and SVA'
)
CODE <- synStore(CODE)

### 2017-01-23 code/Rmd/ROSMAP_RNASeq_Reprocessed_TMM.Rmd
Added folder annotations to the markdown code

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "ROSMAP Reprocessed RNASeq TMM (Based on cogdx)", parentId = parentId)
CODE <- synStore(CODE)

>>>>

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "ROSMAP Reprocessed RNASeq TMM (Based on cogdx)", parentId = parentId)
annotations(CODE) = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'Reprocessed RNAseq',

  tissueTypeAbrv	= 'DLPFC', 
  study = 'ROSMAP', 
  center = 'BROAD-RUSH',

  organism = 'HomoSapiens',
  consortium	= 'AMP-AD',

  normalizationStatus	= TRUE,
  modelSystem	= FALSE,

  normalizationType	= 'TMM'
)
CODE <- synStore(CODE)

### 2017-01-23 code/Rmd/ROSMAP_RNASeq_Reprocessed_TMM_SVA.Rmd
Added folder annotations to the markdown code

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "ROSMAP Reprocessed RNASeq TMM SVA (Based on cogdx)", parentId = parentId)
CODE <- synStore(CODE)

>>>>

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "ROSMAP Reprocessed RNASeq TMM SVA (Based on cogdx)", parentId = parentId)
annotations(CODE) = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'Reprocessed RNAseq',

  tissueTypeAbrv	= 'DLPFC', 
  study = 'ROSMAP', 
  center = 'BROAD-RUSH',

  organism = 'HomoSapiens',
  consortium	= 'AMP-AD',

  normalizationStatus	= TRUE,
  modelSystem	= FALSE,

  normalizationType	= 'TMM and SVA'
)
CODE <- synStore(CODE)
